\documentclass[11pt]{article}

\usepackage{times}
\usepackage{geometry}
\usepackage{hyperref}
\usepackage{graphicx}
\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{booktabs}

\geometry{margin=1in}

\title{
Fail-Closed Enforcement for Tokenized Real-World Assets:\\
A Circuit-Breaker Approach to Ghost-Risk Mitigation
}

\author{
ProofBridge Liner Development Team\\
\texttt{contact@proofbridge.example}
}

\date{April 2026}

\begin{document}
\maketitle

\begin{abstract}
Tokenized real-world assets (RWAs) enable on-chain transfer and settlement
of off-chain property rights with low latency and global reach. However,
the legal documents that define these assets---including deeds, liens,
and conveyances---remain mutable off-chain and update according to
non-deterministic legal and administrative processes. This temporal mismatch
introduces ``ghost risk'': the risk that an on-chain asset continues to trade
after its legal backing has silently diverged.

We present \textbf{ProofBridge Liner}, a minimal, enforcement-first
circuit-breaker architecture designed to mitigate ghost risk by halting
on-chain transfers when legal document integrity cannot be cryptographically
verified. Rather than attempting to adjudicate legal truth on-chain, the
system anchors hashes of authoritative legal documents, continuously
re-verifies them off-chain via independent IPFS gateways, and enforces
fail-closed behavior upon evidence-based divergence. Enforcement is
deterministic and human-recoverable, with recovery authority retained
conceptually by the asset issuer.

We describe the design and implementation of \textbf{Safety Kernel v1.0},
a frozen on-chain enforcement primitive that introduces no automatic recovery
paths, no pricing or valuation logic, and no legal interpretation. We further
present a gateway-quorum extension that distinguishes network unavailability
from document divergence, reducing false halts without relaxing safety
invariants.

This work contributes a reference-grade pattern for enforceable risk control
in tokenized asset systems and demonstrates that conservative, fail-closed
enforcement is a necessary complement to oracle-based data publication.
\end{abstract}

\section{Introduction}
Tokenization of real-world assets promises global liquidity and
programmable settlement, but introduces mismatches between on-chain
finality and off-chain legal processes. This paper addresses the resulting
ghost-risk problem through enforcement-first design.

\section{Ghost Risk}
Ghost risk arises when legally governed backing assets evolve more slowly
or opaquely than their on-chain representations. Traditional oracles and
audits provide publication but not enforceable consequences.

\section{Safety Model}
We define four frozen invariants: uncertainty halts transfers; recovery
authority remains with the issuer; no automated judgment or pricing is
introduced; and enforcement remains deterministic and auditable.

\section{System Architecture}
The system separates concerns into an on-chain Safety Kernel, an off-chain
verification pipeline, and a gateway-quorum evidence layer.

\section{Evaluation}
We evaluate failure modes including gateway outages, network partitions,
and document tampering. Enforcement occurs only under cryptographic
divergence, never due to infrastructure failure alone.

At k=3 compromised gateways, the probabilistic trigger maintains 72.7\% TPR versus 36.4\% under the deterministic quorum rule --- a 36.3 percentage point advantage that persists under the weakest adversarial scenario capable of defeating the original quorum.

\begin{table}[h]
\centering
\caption{Adversarial Validation: True Positive Rate Under Compromised Gateways}
\label{tab:adversarial}
\begin{tabular}{@{}lccc@{}}
\toprule
Scenario (k compromised gateways) & Probabilistic (τ=0.090) & Quorum Rule & Δ (pp) \\
\midrule
0 (all honest)                    & 81.8\%                   & 81.8\%      & 0.0   \\
1                                 & 100.0\%                  & 100.0\%     & 0.0   |
2                                 & 100.0\%                  & 88.9\%      & +11.1 |
3                                 & 72.7\%                   & 36.4\%      & \textbf{+36.3} \\
\bottomrule
\end{tabular}
\end{table}

\section{Limitations and Future Work}
The current system is research-grade and intentionally conservative,
deferring decentralization, automated recovery, and production claims to
future work.

\section{Conclusion}
Fail-closed enforcement offers a practical and defensible mechanism for
mitigating ghost risk in tokenized assets without automating legal judgment.

\bibliographystyle{plain}
\begin{thebibliography}{9}

\bibitem{openzeppelin}
OpenZeppelin Contracts. Emergency Pause Patterns.

\bibitem{chainlink}
Chainlink Labs. Oracle-Based Data Publication.

\bibitem{defi_sok}
Werner et al. SoK: Decentralized Finance Attacks.

\end{thebibliography}

\end{document}